---
title: "boundsheff"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Overview

boundsheff is an R package containing area boundaries for Sheffield as [simple features](https://r-spatial.github.io/sf/articles/sf1.html).

# Installation  

You can install the development version from GitHub with:

```{r install, eval=FALSE}
# install.packages("devtools")
devtools::install_github("scc-pi/boundsheff")
```

If you work for Sheffield City Council you can install the binary package for Windows from:  

> S:\\BI Team\\ShareToAll\\RPackages

Using RStudio you can does this via the *Tools > Install packages...* menu.

# Sources

The data is from the [ONS Open Geography Portal](https://scc-pi.github.io/notes/spatial-data-sources.html#open-geography), the [SCC AGOL](https://sheffieldcc.maps.arcgis.com/) (ArcGIS Online), or the [SCC Portal](https://sheffieldcitycouncil.cloud.esriuk.com/portal/home/) (ArcGIS Enterprise). The latter is behind the Council's firewall. 

# Sheffield boundaries  

```{r library, message=FALSE}
library(boundsheff)
library(sf)
```

## sf_asc_localities

ASC (Adult Social Care) locality boundaries.

```{r sf_asc_localities}
plot(st_geometry(sf_asc_localities))
```

## sf_nhood

100 neighbourhood boundaries.

```{r sf_nhood}
plot(st_geometry(sf_nhood))
```